Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-13 WSSSPE3/report/wg_main_user_community.tex
adding cite

Mozilla Science maintains a ``Working Open Project Guide'' (\url{http://mozillascience.github.io/leadership-training}). \katznote{should get changed to a cite} From the introduction:
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}

Several books have been written about software communities:
\begin{itemize}
\item ``Art of Community'' by Jono Bacon. \katznote{cite?} We could consider distilling this for scientific software.
\item Iain Larmour, from EPSRC in the UK (EPSRC: https://www.epsrc.ac.uk/) (not sure who from mentioned UK Collaborative Computational Projects (CCP: http://ccp.ac.uk)
\end{itemize}

>>>>

Mozilla Science maintains a ``Working Open Project Guide'' (\url{http://mozillascience.github.io/leadership-training}), the introduction of which states: \katznote{should get changed to a cite}
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}

Several books have been written about software communities:
\begin{itemize}
\item ``Art of Community'' by Jono Bacon~\cite{art-of-community}. We could consider distilling this for scientific software.
\item Iain Larmour, from EPSRC in the UK (EPSRC: https://www.epsrc.ac.uk/) (not sure who from mentioned UK Collaborative Computational Projects (CCP: http://ccp.ac.uk)
\end{itemize}
